Evaluating Covid-19 Short-Term Forecasts using \pkg{scoringutils} in \proglang{R}

### 2021-11-22 tables/forecast-types.tex
update paper

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{4.5cm}}
\toprule
\textbf{Forecast type} & \textbf{Target type} & \textbf{Representation of the predictive distribution}\\
\midrule
Point forecast & continuous \newline  integer \newline  binary & one single number for the predicted outcome\\
\cmidrule{1-3}\pagebreak[0]
 & continuous \newline  integer & predictive samples \newline   quantiles \newline   closed analytical form\\
\cmidrule{2-3}\nopagebreak
\multirow[t]{-2}{3.5cm}{\raggedright\arraybackslash Probabilistic forecast} & binary & binary probabilities\\
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{4.5cm}}
\toprule
\textbf{Forecast type} & \textbf{Target type} & \textbf{Representation of the predictive distribution}\\
\midrule
Point forecast & continuous \newline  discrete \newline  binary & one single number for the predicted outcome\\
\cmidrule{1-3}\pagebreak[0]
\midrule
 & continuous \newline  discrete & predictive samples \newline   quantiles \newline   closed analytical form\\
\cmidrule{2-3}\nopagebreak
\multirow{-2}{3.5cm}{\raggedright\arraybackslash Probabilistic forecast} & binary & binary probabilities\\
\bottomrule
\end{longtable}

### 2021-11-22 tables/scores-table-summary.Rnw
update paper

crps <- list(
  `Metric` = "CRPS (Continuous) ranked probability score", 
  `Target types` = r"(continuous, integer)", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, global, stable handling of outliers",
  `References` = ""
)

log_score <- list(
  `Metric` = "Log score", 
  `Target types` = r"(continuous, (integer not in scoringutils))", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, local, unstable for outliers",
  `References` = ""
)

wis <- list(
  Metric = "WIS (Weighted) interval score", 
  `Target types` = r"(continuous, integer)", 
  `Forecast formats` = r"(quantile or interval predictions)",
  `Properties` = "proper scoring rule, global, stable handling of outliers, converges to crps",
  `References` = ""
)

dss <- list(
  `Metric` = "DSS Dawid-Sebastiani score", 
  `Target types` = r"(continuous, integer)", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, somewhat global, somewhat stable handling of outliers",
  `References` = ""
)

brier_score <- list(
  `Metric` = "Brier score", 
  `Target types` = r"(binary)", 
  `Forecast formats` = r"(binary probabilities)",
  `Properties` = "proper scoring rule",
  `References` = ""
)

interval_coverage <- list(
  `Metric` = "Interval coverage", 
  `Target types` = r"(continuous, integer)", 
  `Forecast formats` = r"(interval forecasts (needs matching quantiles))",
  `Properties` = "measure for calibration",
  `References` = ""
)

quantile_coverage <- list(
  `Metric` = "Quantile coverage", 
  `Target types` = r"(continuous, integer)", 
  `Forecast formats` = r"(quantile or interval forecasts)",
  `Properties` = "measure for calibration",
  `References` = ""
)

sharpness <- list(
  `Metric` = "Sharpness", 
  `Target types` = r"(continuous, integer)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "measures sharpness, slightly different depending on forecast format",
  `References` = ""
)

bias <- list(
  `Metric` = "Bias", 
  `Target types` = r"(continuous, integer, quantile)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "captures tendency to over-or underpredict (aspect of calibration)",
  `References` = ""
)

pit <- list(
  `Metric` = "Probability integral transform (PIT)",
  `Target types` = r"(continuous, integer, quantile)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "assesses calibration",
  `References` = ""
)

@@

saveRDS(data, file = "tables/scores-table-summary.rds")

@@

>>>>

# create checkmark with $\checkmark$

crps <- list(
  `Metric` = "(Continuous) ranked probability score (CRPS)", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, global, stable handling of outliers",
  `References` = ""
)

log_score <- list(
  `Metric` = "Log score (logS)", 
  `Target types` = r"(continuous, (discrete not in scoringutils))", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, local, unstable for outliers",
  `References` = ""
)

wis <- list(
  Metric = "(Weighted) interval score (WIS)", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(quantile or interval predictions)",
  `Properties` = "proper scoring rule, global, stable handling of outliers, converges to crps",
  `References` = ""
)

dss <- list(
  `Metric` = "Dawid-Sebastiani score (DSS)", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(closed-form, samples (approximation))",
  `Properties` = "proper scoring rule, somewhat global, somewhat stable handling of outliers",
  `References` = ""
)

brier_score <- list(
  `Metric` = "Brier score (BS)", 
  `Target types` = r"(binary)", 
  `Forecast formats` = r"(binary probabilities)",
  `Properties` = "proper scoring rule",
  `References` = ""
)

interval_coverage <- list(
  `Metric` = "Interval coverage", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(interval forecasts (needs matching quantiles))",
  `Properties` = "measure for calibration",
  `References` = ""
)

quantile_coverage <- list(
  `Metric` = "Quantile coverage", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(quantile or interval forecasts)",
  `Properties` = "measure for calibration",
  `References` = ""
)

sharpness <- list(
  `Metric` = "Sharpness", 
  `Target types` = r"(continuous, discrete)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "measures sharpness, slightly different depending on forecast format",
  `References` = ""
)

bias <- list(
  `Metric` = "Bias", 
  `Target types` = r"(continuous, discrete, quantile)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "captures tendency to over-or underpredict (aspect of calibration)",
  `References` = ""
)

pit <- list(
  `Metric` = "Probability integral transform (PIT)",
  `Target types` = r"(continuous, discrete, quantile)", 
  `Forecast formats` = r"(closed-form, samples, quantile or interval forecasts)",
  `Properties` = "assesses calibration",
  `References` = ""
)

@@

# saveRDS(data, file = "tables/scores-table-summary.rds")

@@

<<table2, echo=FALSE, results=tex>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
library(data.table)

# create checkmark with $\checkmark$

crps <- list(
  `Metric` = "(Continuous) ranked probability score (CRPS)", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"()",
  `Properties` = "proper scoring rule, global, stable handling of outliers",
  `References` = ""
)

log_score <- list(
  `Metric` = "Log score (logS)", 
  `Discrete` = r"(($\checkmark$))",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"()",
  `Properties` = "proper scoring rule, local, unstable for outliers",
  `References` = ""
)

wis <- list(
  Metric = "(Weighted) interval score (WIS)", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"()",
  `Samples (approx.)` = r"(THINK )",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "proper scoring rule, global, stable handling of outliers, converges to crps",
  `References` = ""
)

dss <- list(
  `Metric` = "Dawid-Sebastiani score (DSS)", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"()",
  `Properties` = "proper scoring rule, somewhat global, somewhat stable handling of outliers",
  `References` = ""
)

brier_score <- list(
  `Metric` = "Brier score (BS)", 
  `Discrete` = r"()",
  `Continuous` = r"()",
  `Binary` = r"($\checkmark$)",
  `Closed-form` = r"()",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"()",
  #`Forecast formats` = r"(binary probabilities)",
  `Properties` = "proper scoring rule",
  `References` = ""
)

interval_coverage <- list(
  `Metric` = "Interval coverage", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"()",
  `Samples (approx.)` = r"(THINK )",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "measure for calibration",
  `References` = ""
)

quantile_coverage <- list(
  `Metric` = "Quantile coverage", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"()",
  `Samples (approx.)` = r"(THINK )",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "measure for calibration",
  `References` = ""
)

sharpness <- list(
  `Metric` = "Sharpness", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "measures forecast dispersions",
  `References` = ""
)

bias <- list(
  `Metric` = "Bias", 
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"($\checkmark$???)",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "captures tendency to over-or underpredict (aspect of calibration)",
  `References` = ""
)

pit <- list(
  `Metric` = "Probability integral transform (PIT)",
  `Discrete` = r"($\checkmark$)",
  `Continuous` = r"($\checkmark$)",
  `Binary` = r"()",
  `Closed-form` = r"($\checkmark$)",
  `Samples (approx.)` = r"($\checkmark$)",
  `Quantiles` = r"($\checkmark$)",
  `Properties` = "assesses calibration",
  `References` = ""
)

mean_score_ratio <- list(
  `Metric` = "Mean score ratio", 
  `Discrete` = r"(depends)",
  `Continuous` = r"(depends)",
  `Binary` = r"(depends)",
  `Closed-form` = r"(depends)",
  `Samples (approx.)` = r"(depends)",
  `Quantiles` = r"(depends)",
  `Properties` = "compares performance of two models",
  `References` = ""
)

relative_skill <- list(
  `Metric` = "Relative skill", 
  `Discrete` = r"(depends)",
  `Continuous` = r"(depends)",
  `Binary` = r"(depends)",
  `Closed-form` = r"(depends)",
  `Samples (approx.)` = r"(depends)",
  `Quantiles` = r"(depends)",
  `Properties` = "Ranks models based on pairwise comparisons",
  `References` = ""
)

# saveRDS(data, file = "tables/scores-table-summary2.rds")

library(kableExtra)
library(magrittr)
library(knitr)
data[, 1:8] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  longtable = TRUE,
                  align = c("lccccccl"),
                  linesep = c('\\addlinespace')) %>%
  kableExtra::column_spec(1, width = "3.2cm") %>%
  kableExtra::column_spec(2, width = "1.5cm") %>%
  kableExtra::column_spec(3, width = "1.5cm") %>%
  kableExtra::column_spec(4, width = "1.3cm") %>%
  kableExtra::column_spec(5, width = "1.3cm") %>%
  kableExtra::column_spec(6, width = "1.5cm") %>%
  kableExtra::column_spec(7, width = "1.3cm") %>%
  kableExtra::column_spec(8, width = "6.0cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) %>%
  kableExtra::landscape()

### 2021-11-22 tables/scores-table-summary.tex
update paper

\documentclass{article}
\usepackage{booktabs}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{xcolor}
% \usepackage{colortbl}
\usepackage{float}
\usepackage{longtable}
\usepackage{Sweave}
\begin{document}

@@

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{CRPS (Continuous) ranked probability score} & \cellcolor{gray!6}{continuous, integer} & \cellcolor{gray!6}{closed-form, samples (approximation)} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers}\\
\addlinespace
Log score & continuous, (integer not in scoringutils) & closed-form, samples (approximation) & proper scoring rule, local, unstable for outliers\\
\addlinespace
\cellcolor{gray!6}{WIS (Weighted) interval score} & \cellcolor{gray!6}{continuous, integer} & \cellcolor{gray!6}{quantile or interval predictions} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers, converges to crps}\\
\addlinespace
DSS Dawid-Sebastiani score & continuous, integer & closed-form, samples (approximation) & proper scoring rule, somewhat global, somewhat stable handling of outliers\\
\addlinespace
\cellcolor{gray!6}{Brier score} & \cellcolor{gray!6}{binary} & \cellcolor{gray!6}{binary probabilities} & \cellcolor{gray!6}{proper scoring rule}\\
\addlinespace
Interval coverage & continuous, integer & interval forecasts (needs matching quantiles) & measure for calibration\\
\addlinespace
\cellcolor{gray!6}{Quantile coverage} & \cellcolor{gray!6}{continuous, integer} & \cellcolor{gray!6}{quantile or interval forecasts} & \cellcolor{gray!6}{measure for calibration}\\
\addlinespace
Probability integral transform (PIT) & continuous, integer, quantile & closed-form, samples, quantile or interval forecasts & assesses calibration\\
\addlinespace
\cellcolor{gray!6}{Sharpness} & \cellcolor{gray!6}{continuous, integer} & \cellcolor{gray!6}{closed-form, samples, quantile or interval forecasts} & \cellcolor{gray!6}{measures sharpness, slightly different depending on forecast format}\\
\addlinespace
Bias & continuous, integer, quantile & closed-form, samples, quantile or interval forecasts & captures tendency to over-or underpredict (aspect of calibration)\\
\addlinespace
\cellcolor{gray!6}{Mean score ratio} & \cellcolor{gray!6}{depends on score} & \cellcolor{gray!6}{depends on score} & \cellcolor{gray!6}{compares performance of two models}\\
\addlinespace
Relative skill & depends on scored & depends on score & Ranks models based on pairwise comparisons\\*
\end{longtable}

>>>>

\documentclass{article}
\usepackage{booktabs}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{float}
\usepackage{longtable}
\usepackage{Sweave}
\begin{document}

@@

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{(Continuous) ranked probability score (CRPS)} & \cellcolor{gray!6}{continuous, discrete} & \cellcolor{gray!6}{closed-form, samples (approximation)} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers}\\
\addlinespace
Log score (logS) & continuous, (discrete not in scoringutils) & closed-form, samples (approximation) & proper scoring rule, local, unstable for outliers\\
\addlinespace
\cellcolor{gray!6}{(Weighted) interval score (WIS)} & \cellcolor{gray!6}{continuous, discrete} & \cellcolor{gray!6}{quantile or interval predictions} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers, converges to crps}\\
\addlinespace
Dawid-Sebastiani score (DSS) & continuous, discrete & closed-form, samples (approximation) & proper scoring rule, somewhat global, somewhat stable handling of outliers\\
\addlinespace
\cellcolor{gray!6}{Brier score (BS)} & \cellcolor{gray!6}{binary} & \cellcolor{gray!6}{binary probabilities} & \cellcolor{gray!6}{proper scoring rule}\\
\addlinespace
Interval coverage & continuous, discrete & interval forecasts (needs matching quantiles) & measure for calibration\\
\addlinespace
\cellcolor{gray!6}{Quantile coverage} & \cellcolor{gray!6}{continuous, discrete} & \cellcolor{gray!6}{quantile or interval forecasts} & \cellcolor{gray!6}{measure for calibration}\\
\addlinespace
Probability integral transform (PIT) & continuous, discrete, quantile & closed-form, samples, quantile or interval forecasts & assesses calibration\\
\addlinespace
\cellcolor{gray!6}{Sharpness} & \cellcolor{gray!6}{continuous, discrete} & \cellcolor{gray!6}{closed-form, samples, quantile or interval forecasts} & \cellcolor{gray!6}{measures sharpness, slightly different depending on forecast format}\\
\addlinespace
Bias & continuous, discrete, quantile & closed-form, samples, quantile or interval forecasts & captures tendency to over-or underpredict (aspect of calibration)\\
\addlinespace
\cellcolor{gray!6}{Mean score ratio} & \cellcolor{gray!6}{depends on score} & \cellcolor{gray!6}{depends on score} & \cellcolor{gray!6}{compares performance of two models}\\
\addlinespace
Relative skill & depends on scored & depends on score & Ranks models based on pairwise comparisons\\*
\end{longtable}
\begin{landscape}
\begin{longtable}[t]{>{\raggedright\arraybackslash}p{3.2cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.3cm}>{\raggedright\arraybackslash}p{6.0cm}}
\toprule
Metric & Discrete & Continuous & Binary & Closed-form & Samples (approx.) & Quantiles & Properties\\
\midrule
\endfirsthead
\multicolumn{8}{@{}l}{\textit{(continued)}}\\
\toprule
Metric & Discrete & Continuous & Binary & Closed-form & Samples (approx.) & Quantiles & Properties\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{(Continuous) ranked probability score (CRPS)} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers}\\
\addlinespace
Log score (logS) & ($\checkmark$) & $\checkmark$ &  & $\checkmark$ & $\checkmark$ &  & proper scoring rule, local, unstable for outliers\\
\addlinespace
\cellcolor{gray!6}{(Weighted) interval score (WIS)} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{THINK} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{proper scoring rule, global, stable handling of outliers, converges to crps}\\
\addlinespace
Dawid-Sebastiani score (DSS) & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ &  & proper scoring rule, somewhat global, somewhat stable handling of outliers\\
\addlinespace
\cellcolor{gray!6}{Brier score (BS)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{proper scoring rule}\\
\addlinespace
Interval coverage & $\checkmark$ & $\checkmark$ &  &  & THINK & $\checkmark$ & measure for calibration\\
\addlinespace
\cellcolor{gray!6}{Quantile coverage} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{THINK} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{measure for calibration}\\
\addlinespace
Probability integral transform (PIT) & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & assesses calibration\\
\addlinespace
\cellcolor{gray!6}{Sharpness} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{$\checkmark$} & \cellcolor{gray!6}{measures forecast dispersions}\\
\addlinespace
Bias & $\checkmark$ & $\checkmark$ & $\checkmark$??? & $\checkmark$ & $\checkmark$ & $\checkmark$ & captures tendency to over-or underpredict (aspect of calibration)\\
\addlinespace
\cellcolor{gray!6}{Mean score ratio} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{depends} & \cellcolor{gray!6}{compares performance of two models}\\
\addlinespace
Relative skill & depends & depends & depends & depends & depends & depends & Ranks models based on pairwise comparisons\\*
\end{longtable}
\end{landscape}
